\chapter{Project Description}
\label{ch:project-description}
In today's fast-paced world, efficient management of appointments and services is crucial for small businesses to thrive\footcite[][]{missing}.
With the increasing reliance on digital solutions, a web-based booking system can significantly streamline the process of managing appointments, reducing administrative burdens, and enhancing customer satisfaction\footcite[][]{missing}.
This project aims to develop an online booking system tailored for small businesses, providing an intuitive interface for clients to book services and a robust backend for business owners to manage their offerings.

\section{Purpose of the Project}
\label{sec:purpose-of-the-project}
The primary purpose of this project is to develop an online booking system that enables small businesses to manage appointments and services efficiently. The system will facilitate seamless interaction between clients and business owners, allowing clients to book services at their convenience and business owners to manage their schedules and services with ease. By leveraging ASP.NET and SQL Server, the project aims to deliver a secure, reliable, and user-friendly web application that addresses the specific needs of small businesses.

\subsection*{Objectives:}
\label{subsec:pj-objectives}
The project aims to achieve the following objectives:
\begin{itemize}
    \item \textbf{Enhance Customer Experience:} Provide a simple and intuitive platform for clients to book services, view availability, and manage their appointments online.
    \item \textbf{Improve Operational Efficiency:} Enable business owners to efficiently manage their services, schedules, and client appointments, reducing the time and effort required for administrative tasks.
    \item \textbf{Ensure Data Security:} Implement robust authentication and authorization mechanisms to protect sensitive user data and ensure secure access to the system.
    \item \textbf{Scalability:} Design the system to be scalable, allowing for easy expansion as the business grows and the number of users increases.
\end{itemize}

\section{Scope of the Work}
\label{sec:scope-of-the-work}
This section outlines the current business situation and how the proposed system will address existing challenges and improve operations.

\subsection*{Current Business Situation:}
\label{subsec:current-business-situation}
Many small businesses, such as salons, dental offices, personal trainers, and similar service providers, still rely on traditional methods for managing appointments. These methods often involve manual entry in appointment books, phone calls, and paper records, which can be time-consuming, error-prone, and inefficient. Clients must often call or visit the business premises to book an appointment, which can be inconvenient and result in lost business opportunities if calls are missed or times are not available.

\subsection*{Current Problems:}
\label{subsec:current-problems}
The current appointment management process faces several challenges, including:
\begin{itemize}
    \item \textbf{Inefficiency:} Manual appointment scheduling is labor-intensive and prone to errors, leading to double bookings or missed appointments.
    \item \textbf{Limited Accessibility:} Clients must book appointments during business hours, which can be inconvenient and limit the business's ability to attract new clients.
    \item \textbf{Poor Reecord-Keeping:} Paper-based records are susceptible to loss, damage, and unauthorized access, compromising data integrity and security.
    \item \textbf{Administrative Burden:} Business owners and staff spend a significant amount of time managing appointments, which could be better spent on providing services and growing the business.
\end{itemize}

\subsection*{Proposed Solution:}
\label{subsec:proposed-solution}
The proposed online booking system will address these challenges by providing a digital platform for managing appointments and services. The system will include the following features:

\begin{itemize}
    \item \textbf{User Registration and Authentication:} Secure registration and login for clients and business owners, with role-based access control.
    \item \textbf{Service Management:} Business owners can add, modify, and delete services, as well as set availability schedules.
    \item \textbf{Appointment Booking:} Clients can view available services, book appointments, and manage their bookings online.
    \item \textbf{Admin Dashboard:} Business owners can view and manage all appointments, modify bookings, and access client information through a comprehensive dashboard.
    \item \textbf{Data Security:} Implementing robust security measures to protect user data and ensure secure transactions.
\end{itemize}

The implementation of this system will result in improved operational efficiency, enhanced customer satisfaction, and better data management for small businesses. By transitioning to a digital solution, businesses can reduce administrative burdens, minimize errors, and provide a more convenient and accessible booking experience for their clients.

\section{System Requirements}
\label{sec:system-requirements}
    \rowcolors{1}{primary!25}{primary!15}
    \large
    \begin{tabular}{m{0.20\textwidth}|m{0.65\textwidth}}
        \textbf{Project Sponsor} & The project is sponsored by the small businesses that will benefit from an efficient and modern appointment management system. \\\hline
        \textbf{Business Need} & Small businesses require a digital transformation to manage appointments and services more efficiently, moving away from manual and error-prone methods to enhance accessibility and improve administrative operations. \\\hline
        \textbf{Business Requirements} & The system must allow for user authentication, service management, online appointment booking, and provide an admin dashboard for comprehensive management. It should also ensure data security and be scalable to accommodate growth. \\\hline
        \textbf{Business Value} & Implementing the online booking system will streamline appointment management, reduce administrative overhead, improve customer satisfaction by providing a more accessible service interface, and potentially increase revenue through better service and time management. \\\hline
        \textbf{Special Issues or Constraints} & The project must adhere to a strict timeline, with only few weeks available for development. It requires careful management of resources and priorities to ensure all essential features are implemented without compromising quality. Additionally, the system must be developed within the constraints of the free tiers of technology platforms used, avoiding any cost.


    \end{tabular}